\documentclass[11pt]{article}

%\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{graphicx}

\def\eq1{\mathbb{N}}

\begin{document}

\title{Assignment 2 \LaTeX \ Document}
%\author{by: Ross Gatih}
\date{\today}
\maketitle

%\tableofcontents

\section{All Tables}
\textbf{department}( \underline{dcode}, dname)\\
\textbf{student}(\underline{sid}, slastname, sfirstname, sex, age, dcode, yearofstudy)\\
\textbf{instructor}(\underline{iid}, ilastname, ifirstname, idegree, dcode)\\
\textbf{course}(\underline{cid}, \underline{dcode},	cname)\\
\textbf{courseSection}(\underline{csid}, cid, dcode, year, semester, section, iid)\\
\textbf{studentCourse}(\underline{sid}, \underline{csid}, grade)\\
\textbf{prerequisites}(\underline{cid}, \underline{dcode}, \underline{pcid}, \underline{pdcode})

\section{Queries}

\subsection{Number of female students}

CORRECTION. SUM should be COUNT.

Find the number of female students in the 'Computer Science' department who are in their
fourth year of study.\\
~\\
\textbf{SELECT SUM}(s.sid) \textbf{AS} num\\
\textbf{FROM} student s, department d\\
\textbf{WHERE} s.dcode = d.dcode \textbf{AND}\\
s.sex = 'F' \textbf{AND}\\
s.yearofstudy = 4 \textbf{AND}\\
d.dname = 'Computer Science'

\subsection{Highest number of instructors}

COR. MAX(SUM(i.iid)) bad syntax: can't nest aggregate functions.

Find the department with the highest number of instructors who do not have a PHD degree.
If there is a tie, return all tied departments.\\
~\\
\textbf{SELECT} d.dname \textbf{AS} dname\\
\textbf{FROM} department d, instructor i\\
\textbf{WHERE} d.dcode = i.dcode \textbf{AND}\\
i.idegree != 'PHD'\\
\textbf{GROUP BY} d.dname\\
\textbf{HAVING} \textbf{MAX}(\textbf{SUM}(i.iid))

\subsection{Best student}

COR. Why is cs1.year = 5 and cs1.semester = 9? Same aggregate function nesting problem as previous.

For each department find the best student. A student’s rank is determined by his or her average grade on all of the courses they have completed. Courses for the current semester should not be included. (Hint: The current semester occurs in the largest year/term value.) If there is a tie for first place, include all students in the tie.\\
~\\
\textbf{CREATE VIEW} completedSections \textbf{AS}\\
(\textbf{SELECT} cS.csid, cS.dcode\\
\textbf{FROM} courseSelection cS)\\
\textbf{EXCEPT}\\
(\textbf{SELECT} cS1.csid, cS1.dcode\\
\textbf{FROM} courseSelection cS1\\
\textbf{WHERE} cS1.year = 5 \textbf{AND}\\
cS1.semester = 9)\\
~\\
\textbf{SELECT} d.dname \textbf{AS} dept, s.sid \textbf{AS} sid, s.sfirstname \textbf{AS} sfirstname,\\ s.slastname \textbf{AS} slastname, \textbf{AVG}(\textbf{SUM}(sC.grade)) \textbf{AS} avgGrade \\
\textbf{FROM} department d, student s, studentCourse sC, completedSections cS\\
\textbf{WHERE} s.sid = sC.sid \textbf{AND}\\
sC.csid = cS.csid \textbf{AND}\\
cS.dcode = d.dcode\\
\textbf{GROUP BY} s.sid, d.dname\\
\textbf{HAVING} \textbf{MAX}(\textbf{AVG}(\textbf{SUM}(sC.grade)))\\

\subsection{Courses in Computer Science}

COR. Why GROUP BY? Other than that the query returns courses offered in the summer, not courses that are offered only in the summer.

Find all the courses in 'Computer Science' department that have been taught only in the summer semester. Do not report duplicates.\\
~\\
\textbf{SELECT} c.cname \textbf{AS} cname\\
\textbf{FROM} department d, courseSection cS, course c\\
\textbf{WHERE} cS.cid = c.cid \textbf{AND}\\
c.dcode = d.dcode \textbf{AND}\\
cS.semester = 5 \textbf{AND}\\
d.dname = 'Computer Science'\\
\textbf{GROUP BY} cS.csid
\end{document}
